Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-04-06 ms.tex
I added some descriptions of how I did photometric reduction.
I added a figure to show example Gaussian 2d centering.

\section{Previous Observations}

@@

\section{Time Series}

@@

The initial time series has huge fluctuations (and even goes negative! due to poor aperture centering at the start).
I used \texttt{photutils.centroid\_2g} to do 2D Gaussian centroiding to choose the aperture positions to start with.
Adding a centroiding routine significantly improves the precision as seen in Figure \ref{fig:secTseries}.

@@

>>>>

\subsection{Previous Observations}

@@

\subsection{Photometric Pipeline}

For the photometric reduction, I used the \texttt{ccdproc} package to generate master flat field and bias files.
I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.

@@

The initial time series has huge fluctuations (and even goes negative! due to poor aperture centering at the start).
I used \texttt{photutils.centroid\_2g} to do 2D Gaussian centroiding to choose the aperture positions to start with.
The guess position and \texttt{centroid\_2g} position for the target \sha\ are shown in Figure \ref{fig:centroid2g}.
Adding a centroiding routine significantly improves the precision as seen in Figure \ref{fig:secTseries}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{centering.pdf}
\caption{The guess position of (750.7,682.4) is shown as a cyan circle. The \texttt{centroid\_2g} position of (749.7,681.1) is shown as a red circle.}\label{fig:centroid2g}
\end{centering}
\end{figure}

@@

\clearpage
